Empirical Bayes analysis for detection of gene heterosis in RNAseq data

### 2014-12-17 ebayes_rnaseq_heterosis.tex
added preref to section 4
ji paragraph added

% WML: Since you mainly talk about phenotypic heterosis, I added a little clarification about gene-expression heterosis. However, the reader will still be mostly focused on phenotypic heterosis, and more may need to be done to refocus on the transcriptome. Do we have good real-world examples of heterosis in the expression important or interesting genes? This may be a good question for Dan.

Recently \citep{ji2014estimation} provided an approach to assess heterosis using micro-array data using a hierarchical model for the ...

@@

To assess the efficacy of our method to identify genes demonstrating heterosis, we used a maize data set with parental varieties B73 and Mo17 and the hybrid variety (B73 $\times$ Mo17) \citep{paschold2012complementation}. We compared our method to approaches using the R packages {\tt edgeR}, {\tt baySeq}, and {\tt ShrinkBayes}.

>>>>

Recently, \citep{ji2014estimation} introduced an approach to assess gene heterosis using micro-array data where the response is assumed to be continuous. They built a hierarchical model for gene expression that allows borrowing of information across genes for means and variances. They introduced an empirical Bayes framework that first estimates model hyperparameters, then estimates the posterior distribution for gene-specific parameters, and finally computes heterosis probabilities based on integrals of regions under this posterior.

@@

To assess the efficacy of our method to identify genes demonstrating heterosis, we used a maize data set with parental varieties B73 and Mo17 and the hybrid variety (B73 $\times$ Mo17) \citep{paschold2012complementation}. Details of these data set are available in Section \ref{s:maize}. We compared our method to approaches using the R packages {\tt edgeR}, {\tt baySeq}, and {\tt ShrinkBayes}.
